---
title: "DDP WEEK4"
author: "Grissel"
date: "11/6/2020"

---

## Developing Data wek 4 assignment

This is the presentation for the final week that is week 4 of developing data products coursera subject.
This involves server.R and UI.R file. it is a user interface program. This preentation is part of the coursework.
The link is https://grissel-99.shinyapps.io/ddpweek4/. The code can be found at https://github.com/Grissel-99/developing_data
The above links provided contains all the necessary file for this project.
It links are for my github and shinyapps account.
This is oneof the last courses in the data science coursera.
the csv files used here is related to cars comprising many columns and rows.


# View

plotting graph for different hp values

```{r }
cars <- read.csv('auto-mpg.csv')
head(cars)
```

## code for UI

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}
library(shiny)

shinyUI(
  navbarPage("Analysis of technical specifications",
             tabPanel("Analysis",
                      fluidPage(
                        titlePanel("factors and acc relation"),
                        sidebarLayout(
                          sidebarPanel(
                            selectInput("variable", "Var:",
                                        c("MPG" = "mpg",
                                          "Number of cylinders" = "cyl",
                                          "Displacement (cu.in.)" = "disp",
                                          "Weight (lb/1000)" = "w",
                                          "acceleration (sec)" = "acc"
                                        ))
                          ),
                          
                          mainPanel(
                            h3(textOutput("caption")),
                            
                            tabsetPanel(type = "tabs", 
                                        tabPanel("Plot", plotOutput("cBP"))
                            )
                          )
                        )
                      )
             ),
             tabPanel("About the Data Set",
                      
                      h3("Kaggle autompg-data"),
                      helpText("'Auto-MPG' is used datasetto understand how wt, hpand no. of cyl affects the acc of car.",
                               "dataset contains the specifications vehicles. UCI Machine Learning Repository is where the",
                               "dataset related to the car specification is downloaded."),
                      
                      h3("Important"),
                      p("this dataframe contains 398 observations. these onservations are on 6 vars."),
                      
                      a(" https://archive.ics.uci.edu/ml/datasets/auto+mpg")
             ),
             tabPanel("More detail on the data",
                      h2("Auto-mpg dataset"),
                      hr(),
                      h3("Description"),
                      helpText("The data is technical spec of cars.",
                               "UCI Machine Learning Repository is where this dataset is downloaded from"),
                      
                      h3("Format"),
                      p("this dataframe contains 398 observations. these onservations are on 6 vars."),
                      
                      p("  [, 1]   mpg         Miles/(US) gallon"),
                      p("  [, 2]	 cylinder	 Number of cylinders"),
                      p("  [, 3]	 displacement	 Displacement (cu.in.)"),
                      p("  [, 4]	 horsepower	 Gross horsepower"),
                      p("  [, 5]	 weight	 Weight(lbs)"),
                      p("  [, 6]   acceleration acceleration(sec)"),
                      h3("Source"),
                      
                      p("This dataset was taken from the StatLib library.",
                        
                        "this library is used in 1983.",
                        "The purpose was to use it in American Statistical Association Exposition.")
             ),
             tabPanel("my github reposiory:",
                      a("https://github.com/Grissel-99/developing_data/tree/main"),
                      hr(),
                    
                      h4("Developing Data is the name of the repo")
             )
  )
)
```


## code for server

```{r echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE}

library(shiny)

c <- read.csv('auto-mpg.csv')

shinyServer(function(input,output)
{
  formulaText <- reactive({
    paste("horsepower ~ ",input$variable)
  })
  
  formulaTextPoint <- reactive({
    paste("horsepower ~", "as.integer(",input$variable,")")
  })
  
  
  output$ca <- renderText({
    formulaText()
  })
  
  output$cBP <-renderPlot({
    plot(as.formula(formulaText()),data = c, outline = input$outliers)
  })
  
  
})
```

